---
title: "How to Use DE_tools"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Outline

My goal is to have a brief walkthrough of the minimized path to differential expression analysis, the different ways in which the functions can be used to break off from the example, and to provide a list of the functions and a brief overview of their intended use.

Each of the functions also indpendently has a docsring (a little comment block) that will describe the different arguments the function expects/can handle and what form you should expect the output to be in.

## Starting a Project

Right now I have the functions all stored in one R file which you can source. The project is small enough and I don't know enough yet about package creation, so these tools have not gotten pieced apart into a package format that I can upload to CRAN. 

Therefore, you probably got the files on a USB drive from me.

Make a project, put the DE_tools.R file in the project, create a new script, follow the walk through code and replace with your data.

```{r cars}
source(DE_tools.R)

# load data

#prep
#run
#visualize

```

